Composable Concurrency Models

### 2016-11-17 slides/slides.tex
Cleaned up some stuff pre-practice talk

    \includegraphics[width=220pt]{../figures/nonatomic}
  \end{frame}

    \includegraphics[width=220pt]{../figures/atomic}
  \end{frame}

@@

    \includegraphics[width=220pt]{../figures/agent}
    \vfill
    \textbf{The agent model:} An isolated thread handles all operations on an object.~\footcite{Swalens2014}
  \end{frame}

@@

    \includegraphics[width=220pt]{../figures/csp}
    \vfill
    \textbf{Communicating sequential processes:} Independent threads communicate synchronously through predefined channels.~\footcite{Hoare1978}
  \end{frame}

@@

    \textbf{How do we know that models are composable?}

@@

    Two models are composable if using them within each other doesn't compromise safety or liveness.~\footcite{Swalens2014}
  \end{frame}

@@

  \section{Proposed abstractions}

@@

    \textbf{What characteristics should a unified abstraction have?}~\footcite{Marr2012}

    \begin{itemize}
      \onslide<1->{
        \item Ownership: All objects are owned by something, so ownership should be supported in a way that supports regulated access.
      }
      \vfill
      \onslide<2->{
        \item Managed mutation and execution: The owner of an object should determine how it be read and modified.
      }
      \vfill
      \onslide<3->{
        \item Leveled access: Threads should either have model-level access or abstraction-level access.
      }
      \vfill
      \onslide<4->{
        \item Enforceability: The model's semantics should be enforced regardless of where the model is used.
      }
    \end{itemize}
  \end{frame}

@@

  \begin{frame}
    \frametitle{Conclusions}
  \end{frame}

>>>>

  \begin{frame}
    \frametitle{Atomic variables}

    \begin{columns}
      \begin{column}{0.5\textwidth}
        \centering
        \includegraphics[width=160pt]{../figures/nonatomic}
      \end{column}
      \hfill
      \begin{column}{0.5\textwidth}
        $x = 23$

        \begin{enumerate}
          \item $A$ reads $x$
          \item $B$ reads $x$
          \item $A$ increments value
          \item $A$ writes incremented value to $x$
          \item $B$ increments value
          \item $B$ writes incremented value to $x$
        \end{enumerate}

        $x = 24$
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}
    \frametitle{Atomic variables}

    \begin{columns}
      \begin{column}{0.5\textwidth}
        \centering
        \includegraphics[width=160pt]{../figures/atomic}
      \end{column}
      \hfill
      \begin{column}{0.5\textwidth}
        $x = 23$

        \begin{enumerate}
          \item $A$ calls \textsc{fetch-and-increment} on $x$
          \item $B$ calls \textsc{fetch-and-increment} on $x$
        \end{enumerate}

        $x = 25$
      \end{column}
    \end{columns}
  \end{frame}

@@

    \includegraphics[width=220pt]{../figures/agent}
    \vfill
    \textbf{Agents:} An isolated thread handles all operations on an object.~\footcite{Swalens2014}
  \end{frame}

@@

    \includegraphics[width=220pt]{../figures/csp}
    \vfill
    \textbf{Communicating sequential processes (CSP):} Independent threads communicate synchronously through predefined channels.~\footcite{Hoare1978}
  \end{frame}

@@

    \textbf{How do we know that models are composable?~\footcite{Swalens2014}}

@@

    Two models are composable if using them within each other doesn't compromise safety or liveness.
  \end{frame}

@@

  \section{Unifying abstractions}

@@

    \textbf{What characteristics should a unifying abstraction have?}~\footcite{Marr2012}

    \begin{itemize}
      \onslide<1->{
        \item Ownership: All objects are owned by something, so ownership should be supported in a way that supports regulated access.
      }
      \vfill
      \onslide<2->{
        \item Managed mutation and execution: The owner of an object should determine how the object should be read and modified.
      }
      \vfill
      \onslide<3->{
        \item Leveled access: Threads should either have model-level access or abstraction-level access.
      }
      \vfill
      \onslide<4->{
        \item Enforceability: The abstraction should be able to enforce all model rules.
      }
    \end{itemize}
  \end{frame}

@@

    \begin{itemize}
      \onslide<1->{
        \item An abstraction like the OBMOP must be implemented at a low level to achieve acceptable performance.
      }
      \vfill
      \onslide<2->{
        \item The OBMOP has some limitations: The owner is the only entity that enforces rules, and the abstraction doesn't guarantee things like freedom from deadlock.
      }
      \vfill
      \onslide<3->{
        \item This approach has potential: The authors were able to implement STM, CSP, agents, and actors in less than 500 total lines of code.
      }
    \end{itemize}
  \end{frame}
